Technical Report

### 2024-03-05 Reports/tech_report1.tex
update report

The running code's file name is \verb*|DiamondLipschitz_V0p7_test.py|. And the partial output file name is \verb*|DL_V0p3_layer7_comparison_layerWeight_0p25.txt|.  It is based on the new pure y-constraints, use MILP model to compute the gamma of layer 7 with open 81 ReLU.

@@

@@

>>>>

The running code's file name is \verb*|DiamondLipschitz_V0p7_test.py|. And the partial output file name is \verb*|DL_V0p3_layer7_comparison_layerWeight_0p25.txt|.  It is based on the new pure y-constraints, use MILP model to compute the gamma of layer 7 with open 47 ReLU.

@@

	\item\emph{Open $\ReLU$ number:} Open 47 ReLU node

@@

\subsection{Compute gamma for layer 7 for normal 5x100, pure y-constraints, with 0.25, using updated code}

This experiment is to compute the gamma of layer 7 normal 5x100 with pure-y constraints constraints, with open 47 node. The major update is that now in the code of finding open ReLU node by compensating, we use $\gamma_i$ instead of $\beta_i$.

The running code's file name is \verb*|DiamondLipschitz_V0p7_test.py|. And the partial output file name is \verb*|DL_V0p7_layer7_comparison_layerWeight_5.txt|.  It is based on the new pure y-constraints, use MILP model to compute the gamma of layer 7 with open 81 ReLU.

\begin{itemize}
	\item\emph{Experiments Id}: 030400302024

	\item\emph{Open $\ReLU$ number:} Open 47 ReLU node

The same as previous experiments, except that when choosing open ReLU nodes in layer 3 and 5, we use $\gamma_i$ instead of $\beta_i$.

\begin{itemize}
	\item \emph{Log:} \verb*|DL_V0p7_layer7_comparison_layerWeight_5.txt|.

	\item \emph{Total time:} 36034s.

	\item \emph{Key results:}  The average gamma of this layer is:  2.7484474999036674

	The average solution for gamma of this layer is:  2.4304639934792

	\item  \emph{Binary output}: The gamma of layer 7 is stored in the file \verb*|Diamond_record_6_100_dictionary_with_end_layer7_2024_03_04_15_32_38.b|.
